---
title: "Lexa Database Schema"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Lexa Database Schema}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(lexa)
```

## General structure

A Lexa database (`lexadb`) is a directory containing the following files/dirs:

- `config.yaml`: the database configuration file.
- `grammar.yaml`: the grammar specification file.
- `lexicon/`: directory containing Lexa lexicon files.
- `texts/`: directory containing Lexa text collections (`lexatxt`).

## Lexicon file

```yaml
id: lx_00000n
lexeme: <string>
phon: <string>
morph_category: <lexical, grammatical>
morph_type: <root, stem, affix, clitic, particle, compound, phrase>
part_of_speech: <string>
inflectional_features:
  <feature_n>: <string>
etymology: <string>
loan_word: <string>
notes: [<string>]
allomorphs:
  al_0n:
    id: al_0n
    morph: <string>
    phon: <string>
    conditioning:
      type: <phonological, morphosyntactic, free>
      context: <string>
senses:
  se_0n:
    id: se_0n
    gloss: <string>
    definition: <string>
    literal: <string>
    scientific: <string>
    usage: <string>
    inflectional_features:
      <feature_n>: <string>
    examples: ["tx_00000n"]
    etymology: <string>
crossref: ["lx_00000n"]
variants: [<string>]
semantics:
  semantic_domain: ["sd_00000n"]
  synonyms: ["lx_00000n"]
  antonyms: ["lx_00000n"]
date_created: <date>
date_modified: <date>
```

## Text collection

Texts are located in the `texts/` folder.
Each text is saved in a separate `.yaml` file, with no restrictions on naming (except you must avoid spaces and fancy characters.)

```yaml
id: tx_00000n
title: <string>
topic: <string>
genre: <string>
participants: [<string>]
translators: [<string>]
source: <string>
text:
  st_00000n:
    sentence: <string>
    phon: <string>
    morpho_phon: <string>
    morpho: <string>
    gloss: <string>
    translation: <string>
    literal: <string>
    notes: [<string>]
notes: [<string>]
```

