---
title: "Typesetting interlinear glosses"
output:
  lexa::lexa_html:
    base_format: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Typesetting interlinear glosses}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Overview

Users can output interlinear glosses in Rmarkdown files from the texts in a Lexa database.

Both PDF and HTML output formats are supported.
The LaTeX package [expex](https://ctan.org/pkg/expex) is used for PDF output, while HTML glosses are rendered with [Leipzig.js](https://bdchauvette.net/leipzig.js/).

At this time, the functionalities implemented within lexa are limited, but they provide sufficient coverage for basic glossing.

# Load a Lexa database

To load a Lexa database, we first attach the lexa package.

```{r setup}
library(lexa)
```

And then load the example database `eleryon_lexadb`.

```{r eleryon}
eleryon_path <- system.file("extdata/eleryon_lexadb", package = "lexa")

eleryon <- load_lexadb(eleryon_path)
```

We can now inspect the content of the `eleryon` database.

```{r eleryon-summary}
eleryon
```

# Include interlinear glosses

There are two ways of including an interlinear gloss in an Rmarkdown file.

## Inline R code

One is by using inline R code (see the source of this vignette for the code).

`r include_gloss(eleryon, "tx_000001", "st_000001")`

## R code chunk

Alternatively, one can use an R code chunk and set `results='asis'`.

```{r asis, echo=TRUE, results='asis'}
include_gloss(eleryon, "tx_000001", "st_000002")
```

